\documentclass[11pt]{memoir}

%\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathtools}

\begin{document}
	\input{commands.tex}
	
	\cmt{Intent is that each chapter builds on the last, intended to be progressive. 
		Foundation -> more advanced 
		
		Part 1: Mindset 
		Constructive attitude, taking responsibility for your education and believing in yourself,
		curiosity.
		Habit formation 
		Focus
		Looking after the machinery: exercise, sleep, and diet
		
		Part 2: Learning effectively 
		
		Psychological factors: not being intimidated, burned out, etc.
		Make it smaller and easier.
		Self-critique and self-coaching
		Go with your own style 
		
		Learning principles
		- What is the common thread? 
		- Keep asking why
		- Try to generalise 
		
		Develop a process
		Experiment - try different things
		Aim for progress not perfection 
		Get to the doing as soon as possible
		Dissect
		Break it down more
		Focus on principles 
		Focus on fundamentals 
		break it down
		Prioritise: bang for your buck
		Be goal-oriented
		
		Part 3: Dealing with institutionalisation
		Exams and assignments}
	
	\frontmatter
	\input{title_page.tex}
	\tableofcontents
	\chapter{The purpose of this book}
	\cmt{
		Practicality and effective absorption and implementation. 
		Simplicity, lots of example, concrete exercises. 
	}

	\paragraph{}
	The purpose of this book is to help undergraduates and upper high
	school students to learn more effectively. 
	By writing this book, I hope to help others get the most out of their schools, and in
	some cases, to learn skills and knowledge \emph{in spite} of their schools.
	When I say education, I mean the gaining of understanding, skills, and perspective, 
	through whatever means - I do not mean a fancy piece of paper stamped with the logo of a university. As such, this is a book primarily on \emph{learning}, and I will only 
	briefly cover topics such as test-taking and doing assignments. 
	
	\paragraph{}
	I intend for this book to be useful for students from a variety of different educational
	and personal backgrounds attending many different types of institutions. Therefore I
	have written about principles which I think apply to learning just about anything at
	just about any place, and left out content that I think may be specific to any one field
	of endeavour or any one institution. However, for the sake of concreteness, I will use 
	examples from mathematics, computer science, drawing, and martial arts when necessary. 
	I hope this will be a sufficiently broad range of examples that most readers will be 
	able to understand this book. 
	
	\section{Author's qualifications}
	\paragraph{}
	What makes me qualified to write such a book? In high school I completed the 
	International Baccalaureate programming, graduating with the maximum score of 45.
	This placed me in the op 0.05\% of the nation's high school graduates. In the last
	3 years of high school, I was the top student in my grade, and in grade 11, I won the
	subject award for every subject I studied. At university, I majored in mathematics and
	computer science, graduating with the award for highest score in pure mathematics, the
	university medal, and a final-year GPA of 7 out of 7. I am not particularly intelligent
	or talented, but I have figured out how to do well within the education system. 
	Furthermore, I have tutored a variety of courses at university, so I am familiar with 
	mistakes that students make frequently.
	
	\section{Book organisation}
	\paragraph{}
	In conveying my tips, I want to be as clear, concise, and simple as possible. 
	I have written the book to begin with the most important and foundational concepts. 
	Each chapter depends on the previous chapters, so I encourage you to read the book 
	in order if possible. Each chapter also has an overview at the beginning to highlight the most important lessons of each chapter. 
	
	\paragraph{}
	None of the things that I am about to tell you - and indeed, none of the things that
	I have \emph{ever} learned - can be learned simply by reading. You must apply it in 
	some way; make it your own, absorb and internalise it. I have therefore suggested 
	exercises throughout the book, and hope that you will also invent your own. 
	
	\mainmatter
	\input{mindset.tex}
	\input{goal_setting.tex}
	\input{building_habits.tex}
	\input{focus.tex}
	
	\chapter{Fundamentals}
	Focus on principles and foundations, simplify everything, revise frequently.
	
	\chapter{How to get the most out of uni}
	
	
\end{document}